### 2020-11-26 paper/sections/experiment.tex
design

\subsection{Experiment Setup}
\textbf{Datasets:} Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows. First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd"). Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes. In addition, these videos need to be as dynamic as the real world, such as not standing still for too long. Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy. For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.

Based on the above filtering strategy, we finally selected three datasets:

@@

Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
\subsection{Configure Selection}
We simulate the environment with three object detection models, which are SSD ResNet152V1, FasterRCNN ResNet50V1, FasterRCNN InceptionResNetV2. For each model, two kinds of image resolution for inference, which is $1024\times1024$ and $640\times640$, can be picked up. Besides choosing a proper configure of model and image resolution, AutoConfigure needs to select a proper number of frames per second(fps). We in our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. Therefore, the number of actions that the agent can choose is forty-eight.
\subsection{Experiment Parameters}
We apply deep Q-learning policy to train the agent. In the training procedure, we build up eight independently identical environments for each data set to speed up the training and decrease the dependency of the data. The leaning rate is set to 0.001. The discount factor is set to 0.9. For each dataset, we train the agent 10 epochs and 1000 steps per epoch. The exploration factor is 0.9.
\subsection{Some results}

>>>>

\subsection{Datasets}
\textcolor{note}{this section is too long}

Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows. First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd"). Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes. In addition, these videos need to be as dynamic as the real world, such as not standing still for too long. Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy. For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score.Based on the above filtering strategy, we finally selected three datasets:

@@

Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.

\subsection{Configure Selection}
We simulate the environment with three object detection models, which are SSD ResNet152V1, FasterRCNN ResNet50V1, FasterRCNN InceptionResNetV2. For each model, two kinds of image resolution for inference, which is $1024\times1024$ and $640\times640$, can be picked up. Besides choosing a proper configure of model and image resolution, AutoConfigure needs to select a proper number of frames per second(fps). We in our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. Therefore, the number of actions that the agent can choose is forty-eight.
\subsection{Experiment Parameters}
We apply deep Q-learning policy to train the agent. In the training procedure, we build up eight independently identical environments for each data set to speed up the training and decrease the dependency of the data. The leaning rate is set to 0.001. The discount factor is set to 0.9. For each dataset, we train the agent 10 epochs and 1000 steps per epoch. The exploration factor is 0.9. The inference models are implemented in Tensorflow and are pretrained on standard image datasets \cite{trade-offs}, and the switching of video frame rate and resolution is done by FFmpeg \cite{ffmpeg}.
\subsection{Experiment Results}

### 2020-11-26 paper/sections/introduction.tex
design

\section{Introduction}
\label{Section: introduction}
With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations. The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks. In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{huang2017speed_accuracy}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.

For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics. A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{howard2017mobilenets}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is a video analytics \emph{configuration}. The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}. Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference. Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.

Apparently, choosing different configurations will affect resource consumption and accuracy. For example, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. However, choosing a simple model with low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

The \emph{best} configuration for a video analytics pipeline also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}. Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold. On the one hand, if one only profiles the processing pipeline to choose the best configuration \emph{once}, the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by picking a cheap configuration). On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.

@@

For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules. An automatic approach is needed, one that is able to learn from video contents, to decide what is the best configuration for the current video content. The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem. In our solution, we tackle the following design challenges.

@@

\begin{itemize}	
\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second. As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

@@

\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks. In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contents automatically. 
\end{itemize}

To address the above challenges, we present a content-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contents, thus solving this difficult optimal configuration decision problem in a very low-cost way. The main contributions of this paper are summarized as follows.
\textcolor{note}{zhaoliang add more contributions}

\begin{itemize}	
\item We design an interactive training environment that can be applied to different video analytics applications. We propose an asynchronous advantage actor-critic-based \cite{mnih2016asynchronous} agent to pick the best configuration for video analytics. Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video content.

@@

\item AutoConfigure can achieve xx-xx\% higher accuracy with the
same amount of resources, or achieve the same accuracy
with only xx-xx\% of the resources. Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\% to the overall video analytics pipeline.
\end{itemize}

>>>>

\section{Introduction}
\textcolor{note}{this section is too long}

\label{Section: introduction}
With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations. The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks. In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{trade-offs}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.

For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics. A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is a video analytics \emph{configuration}. The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}. Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference. Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.

Apparently, choosing different configurations will affect resource consumption and accuracy. When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

\begin{figure*}[!t]
	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
	%	\vspace{0.2cm}
	\caption{Framework of AutoConfigure architecture}
	\label{fig: framework}
\end{figure*}

%We use~\autoref{fig2} to support that, the data in this figure come from a real road. It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the decrease of accuracy is partly acceptable.

%As shown in~\autoref{fig1}, at a fixed frame rate, using a complex model with high resolution (such as FasterRCNN+InceptionResnet 1024p) can obviously and accurately detect the target object, but it also requires more computing resources. However, when using the same model, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. Another example is that choosing a simple model with low resolution (such as FasterRCNN+ResNet50 640p) can significantly reduce resource consumption, although it reduces the accuracy to some extent.

%\begin{figure}[h]
%\includegraphics[width=9cm,height=5cm]{figures/figure1.pdf}
%\centering
%\caption{The effect of different models and resolutions on accuracy and processing time at a fixed frame rate.}
%\label{fig1}
%\end{figure}
%
%\begin{figure}[h]
%\includegraphics[width=9cm,height=5cm]{figures/figure2.pdf}
%\centering
%\caption{Under the best model, the accuracy and processing time vary with the different frame rate.}
%\label{fig2}
%\end{figure}

The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}. Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold. On the one hand, if one only profiles the processing pipeline to choose the best configuration \emph{once}, the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by picking a cheap configuration). On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.

@@

For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules. An automatic approach is needed, one that is able to learn from video contexts, to decide what is the best configuration for the current video context. The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem. In our solution, we tackle the following design challenges.

@@

\begin{itemize}	
\item \emph{The best configuration for a video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second. As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

@@

\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks. In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contexts automatically. 
\end{itemize}

To address the above challenges, we present a context-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way. A brief framework of AutoConfigure is shown in Figure~\ref{fig: framework}. \textcolor{note}{some description?} The main contributions of this paper are summarized as follows.

\begin{itemize}	
\item We design an interactive training environment that can be applied to different video analytics applications. We propose an Deep Q-learning Network-based \cite{DQN} agent to pick the best configuration for video analytics. Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video context.

@@

\item AutoConfigure can achieve 20-30\% higher accuracy with the
same amount of resources, or achieve the same accuracy
with only 50-70\% of the resources. Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\%\textcolor{note}{(To be tested)} to the overall video analytics services.
\end{itemize}

### 2020-11-26 paper/sections/relatedwork.tex
minor ab and intro
update 0908
ICME
design

\subsection{Configuration optimization} 
\subsection{Static configuration optimization}
Several previous papers have considered optimizing video analytics pipelines by either adjusting the configuration knobs or training specialized NN models. VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations. VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations. MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingest and video query. By tuning the share of computing resources of both phases, Focus achieves effective and flexible tradeoff of latency and accuracy of video analytics. These algorithms all profile and optimize video analytics only once at the beginning of the video. They do not handle changes in video stream content. But the optimal configurations do change over time because of the complex and changeable video stream contents.

\subsection{Dynamic configuration optimization}
Some papers study how to dynamically optimize the configuration for video analytics when the video stream content changes. \cite{shen2017retrain_model} adaptively retrains the NN model to detect the set of popular objects as it changes over time in the video classification task. \cite{yang2019edge_coordinated} proposes an online video quality and computing resource configuration algorithm to gradually learn the optimal configuration strategy, effectively improving the analytic accuracy while providing the low-latency response. INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations, and makes scaling and resource allocation decisions when application load varies and the available resources vary over time. QuickAdapt \cite{ullah2019quickadapt} uses
descriptive statistics of security events data and fuzzy rules to
enable a Big Data Cyber Security Analytics (BDCA) system to quickly adapt to the changes in security events data. JCAB \cite{wang2020jcab} jointly optimizes configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contents. The online algorithm effectively balances analytics accuracy and energy consumption while keeping low system latency. \cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency. Our framework pays attention to the complex and changeable video stream contents, and picks the best configuration according to current video content.

The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics pipelines, reducing resource consumption with little degradation in accuracy. They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.\cite{jiang2018chameleon} Notice that Chameleon still has non-trivial room for improvement compared to the optimal (idealized) performance, i.e.,
periodic updating with zero profiling cost. Even the search space is linear, and the profiling cost is still expensive. Such a 24-hours video, Chameleon profiles the configuration space once in every profiling window (16s), it would profile 5400 times. One profiling cost grows linear in the number of configuration knobs and the number of values per knob. The total profiling cost is also significantly high, which is equal to one profiling cost multiply the number of profiling (5400). Our solution, called AutoConfigure, leverages a reinforcement learning-agent to automatically choose the best configuration periodically, significantly reducing the cost of profiling since the agent's choosing time is extremely lower.

>>>>

%\subsection{Configuration optimization} 
\subsection{Static configuration optimization}
Several previous papers have considered optimizing video analytics servicess by either adjusting the configuration knobs or training specialized NN models. VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations. VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations. MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingest and video query. By tuning the share of computing resources of both phases, Focus achieves effective and flexible tradeoff of latency and accuracy of video analytics. These algorithms all profile and optimize video analytics only once at the beginning of the video. In their works, video is divided into pictures at a constant frame rate, and the work of video analyzing is regarded as a fixed task either. In other words, they do not handle changes in video stream context. But the optimal configurations do change over time because of the complex and changeable video stream contexts.

\subsection{Dynamic configuration optimization}
Some papers study how to dynamically optimize the configuration for video analytics when the video stream context changes. \cite{shen2017retrain_model} adaptively retrains the NN model to detect the set of popular objects as it changes over time in the video classification task. \cite{yang2019edge_coordinated} proposes an online video quality and computing resource configuration algorithm to gradually learn the optimal configuration strategy, effectively improving the analytic accuracy while providing the low-latency response. INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations, and makes scaling and resource allocation decisions when application load varies and the available resources vary over time. QuickAdapt \cite{ullah2019quickadapt} uses
descriptive statistics of security events data and fuzzy rules to
enable a Big Data Cyber Security Analytics (BDCA) system to quickly adapt to the changes in security events data. JCAB \cite{wang2020jcab} jointly optimizes configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contexts. The online algorithm effectively balances analytics accuracy and energy consumption while keeping low system latency. \cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency. Our framework pays attention to the complex and changeable video stream contexts, and picks the best configuration according to current video context.

The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics servicess, reducing resource consumption with little degradation in accuracy. They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.\cite{jiang2018chameleon} Notice that Chameleon still has non-trivial room for improvement compared to the optimal (idealized) performance, i.e.,
periodic updating with zero profiling cost. Even the search space is linear, and the profiling cost is still expensive. Such a 24-hours video, Chameleon profiles the configuration space once in every profiling window (16s), it would profile 5400 times. One profiling cost grows linear in the number of configuration knobs and the number of values per knob. The total profiling cost is also significantly high, which is equal to one profiling cost multiply the number of profiling (5400). Our solution, called AutoConfigure, leverages a reinforcement learning-agent to automatically choose the best configuration periodically, significantly reducing the cost of profiling since the agent's choosing time is extremely lower.
